---
title: "Clustering Paket"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Clustering Paket}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Clustering)
library(ggplot2)
library(dplyr)
```

This package implements the main clustering algorithms.

Clustering is a main task in unsupervised learning.

In supervised learning, the best known sub discipline of machine learning the aim is to predict the output $\bar{Y}$ of a model given the input variables $\bar{X}$. We achieve this by training a machine learning algorithm on test data $(X_i, Y_i), i=1,..,n$ to which we know the response.

In contrast, unsupervised learning aims to find patterns in a training set $X_i, i=1,...,n$ without any (or minimal) external information and in some cases make predictions based on that. 

This is best illustrated by an example. Let us take a look the `iris` data set. It contains the sepal lengths and widths, petal lengths and widths and species of different irises. If you take a closer look at the petal lengths and widths in relation to the species, we find that they are closely correlated:

```{r, fig.show='hold'}
ggplot() + 
  geom_point(data=iris, aes(x=Petal.Length, y=Petal.Width, color=Species)) +
  theme_bw()
```

Based on this plot we can conduct that irises of the species virginica tend to have large petals while irises of the species setose rather have smaller petals. In the above plot these especies form their on clusters.

The objective of clustering would be to find these clusters - without knowing about the species of the instances. It does not help us to tell which species a specific iris belongs to. But it would tell us, that these irises have something in common and some algorithms even allow us to predict, given a petal length and width, which cluster a new instance would belong to.

There are multiple clustering algorithms, each with its different strengths and weaknesses which will be illustrated here.


## k-means clustering



